SHARP II: Dark Matter Substructure, Gravitational Lens Flux Ratio Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on Disks

### 2015-04-25 papers/B1555_EdgeOn/B1555_letter.tex
Small changes to text

\title[Beware the Effect of Edge-on Disks]{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\\
$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

Gravitational lens flux-ratio anomalies provide a powerful technique
for detecting the presence of dark matter substructure in distant
galaxies.  However, before using the statistics of systems with these
anomalies, it is imperative to ascertain that a given system does not
have properties that could plausibly cause the observed anomaly
without the need for substructure.  In this letter, we present the
case of the B1555+375 lens system, which has a strong radio-wavelength
flux-ratio anomaly but where the lensing galaxy is also revealed in
high-resolution imaging to have a clear edge-on disk component.  The
disk crosses directly over the pair of images that exhibit the
anomaly, and we show that simple models that include the disk can
reproduce the anomaly without requiring substructure.  
Other lens systems that we have observed with adaptive optics imaging
as part of the Strong lensing at High Angular Resolution Programme (SHARP)
show a similar behaviour and will be the subject of a future paper.  
These results suggest that the assumption that
all flux-ratio anomalies are due to substructure will likely overestimate
the substructure fraction in massive galaxies.

@@

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems \citep{Bradac02}. 
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction. This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citep{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure. 
%
An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

While future large-scale surveys, such as the LSST, are expected to
deliver new large samples of gravitationally lensed quasars, in the
near future the discovery of new systems using narrow-line quasar
emission \citep{N14} will provide new invaluable statistical
perspective on current constraints based on flux ratio anomalies.  In
this letter, we explore the idea that not all flux ratio anomalies are
related to the presence of substructure, but that some originate in a
more complex lens galaxy mass distribution than initially
considered. To this end we use new infra-red data from the Strong
lensing at High Angular Resolution Program (SHARP; Fassnacht et al.,
in prep). The main goal of the SHARP project is to re-observe known
quadruple and Einstein ring lens systems at a much higher angular
resolution by making use of observations with (1) adaptive optics (AO)
on the Keck telescopes, (2) the Hubble Space Telescope, and (3) large
interferometric arrays \citep{SHARP12,V12}. In particular, to better
understand the causes of flux ratio anomalies in gravitational lenses
we focus on the B1555+375 lens system\citep{Marlow99}.  This system was
discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
has a pair of merging images that show a strong flux ratio anomaly at
radio wavelengths.  Follow-up observations ruled out radio propagation
effects as the cause of the anomaly \citep{K03,KD04}.  The B1555+375
system was included in both the observational and theoretical analysis
of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
mass distribution is of key importance.  Our analysis makes use of
the new information obtained from the latest SHARP infrared imaging.
The paper is organized as follows: the latest SHARP data are
introduced in section 2; in section 3 we present the lens model while
the results of this analysis and their implications are discussed in
section 4.

@@

To model B1555+375, we use the lens modeling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image
positions and flux densities measured by the radio observations of
\citet{Marlow99}.  These authors present a singular isothermal ellipsoid
(SIE) model that provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A
and B.  \citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  Although
the flux ratio anomaly that is observed in the radio data may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the HST imaging (two rightmost panels in
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux ratio anomaly without the need for substructure.  The edge-on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the lack of detection of these
images.

As a first trail of modelling, we create a single SIE model to 
justify the performance of a simple lensing potential. Consistent with previous studies
\citep{Marlow99, Xu14}, our single elliptical potential model cannot predict flux anomaly in B1555+375. 
We then create two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =1.5$. Our steps to explore the parameter space are: (1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{Marlow99} as the start point of the bulge component and the source position. (2) Let all parameters without priors vary to reach a temporary best-fit. (3) Start with the best-fit in step 2 and let all parameters with priors vary to reach another best-fit (also ensure this best-fit is not far from the priors). (4) Let all parameters vary to reach the final optimal model. 
The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.
{\bf We have not included an external shear component into our model because the constraints provided by the image positions and  fluxes would not be sufficient 
to constrain such a model. However, we note that the image not affected by dust (image C) in the Keck AO data is consistent with negligible shear (i.e. shear strength $\Gamma_s=0.002$), when modelled with the pixelized technique by \citet{V09}.}

@@

Gravitational lensing is,  at present, the most powerful tool for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes, such as propagation effects and assumptions on the mass distribution of the lens galaxy.  
It is for this reason that much of the effort in the flux-ratio technique
has been focused on radio-loud lens systems.  At these wavelengths,
dust extinction and microlensing effects should be minimal
\citep[although see][for a rare example of radio microlensing]{K2000}.
Radio propagation effects can affect radio fluxes, as is clearly shown
in the B0128+437 system \citep{B04}.  However, these propagation
effects can be disentangled from substructure lensing because they
have well known dependencies on wavelength. \citet{KD04} examine all
eight radio loud flux anomalous lenses besides B0128+437, namely: MG
0414+0534, B0712+472, B1359+154, B1422+231, B1555+375, B1608+656,
B1933+503, and B2045+265.  They found no strong wavelength dependence
in the flux ratios of all these systems and therefore rule out radio
propagation effects as significant contributors to the observed
anomalies.

{\bf In this letter, we focus on the effect of more complicated mass distributions for the lens galaxy on flux ratio anomalies.
Traditionally, flux anomalous lensed quasars are radio loud systems that are firstly discovered in radio observations. While radio data provide reliable information on the positions and the fluxes of the lensed images, they are often unable to detect the lens galaxies. Moreover, lens modelling based only on the positions of the four images can be highly degenerate and prior assumptions play a key role in the interpretation of the observed flux ratio anomaly.
Since lens galaxies are mostly located at low redshift, optical and near-infrared observations are ideal to measure the light distribution of lens galaxies and obtain useful prior information  
on the underlying mass distribution. Indeed \citet{SHARP12} has shown that high resolution IR imaging can help to significantly improve the precision of the lens modelling. This improvement is even more dramatic in the case of B1555+375, where HST and SHARP AO high resolution imaging, has allowed us to detect, for the fist time, the presence of an edge-on disk. This new discovered edge-on disk provides a strong prior for our lens modelling.  With a bulge plus an edge-on disk, our models produce matches to both the radio image
positions and their flux ratio, while models with only one SIE component \citep{Marlow99,Xu14} fail to reproduce the fluxes correctly. Our successful modelling indicates that the
kiloparsec-scale structure of the lens galaxy itself is sufficient to explain the flux ratio anomalies in B1555+375, without any need to invoke the presence of substructure.  }

From a theoretical perspective, \citet{Xu14} find that substructures
cannot explain the observed radio flux anomalies in all the lenses
that were considered. By adding subhaloes from numerical simulations
on to these systems, only one out of eight radio loud systems
reproduces the level of flux anomalies seen in the data.  The rest of
them are unlikely (only $1 \% - 4 \%$ probability) to have flux
anomalies produced by substructure, including our target B1555+375.
In fact, among those eight radio lenses, B1555+375 is one of the most
anomalous systems, but it is also one of the most challenging systems
to explain by substructures. \citet{Xu14} have concluded that the failure in
predicting flux ratios is most likely due to oversimplified/improper lens
modelling. They also point out that the SIE component and the external
shear in their model are orthogonal, indicating a possible missing
ingredient in the lens model. Their results are consistent with the SHARP
$K^{\prime}$ band observations, in which an edge-on disk crosses the
radio merging double and which fully accounts for the observed flux ratio anomaly.  In general, it is well known 
\citep[e.g,][]{Ka91} that lens models based only on the locations of lensed
quasar/AGN images have large degeneracies. Therefore, before
concluding that the flux ratios in any given lens system are a result
of substructure, it is critical to explore a range of smooth models
that are informed by additional observations or to do a comprehensive
analysis such as that conducted by \citet{Xu14}. Otherwise, derived
substructure fractions should be considered as upper limits.

@@

\section{Conclusions}
{\bf In this letter we have taken advantage of the power of multi-wavelength high resolution data to investigate whether flux ratio anomalies could be explained by more complex smooth models for the lens galaxy mass distribution rather than substructure. Thanks to new imaging from the SHARP $K^{\prime}$ band observations of the gravitational lens system B1555+375, we have identified the existence of a previously undetected edge-on disk. By including this disk in the mass model of the lens galaxy, we find a good fit for both the positions and flux ratios of the lensed images. Our results clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of a few lensed images, can lead to improper lens models and a misinterpretation of the origin of flux ratio anomalies. 
We stress, therefore, that one should be very careful when interpreting the nature of flux ratio anomalies, as prior assumptions on the lens mass distribution are a significant source of bias. Our analysis shows that in order to derive precise quantification of the substructure population and any derived properties from strongly lensed flux anomalous systems, it is crucial to have a careful estimation of non-substructure effects. In fact, even in the presence of mass substructures, the observed flux ratio anomalies could be still dominated by the complex structure of the lens galaxy. Finally, additional near-infrared AO imaging from SHARP shows that B1555+375 is not the only system having a significant disk component detection in
the lensing galaxy.  These systems will be investigated in future work, but the images alone strongly suggest that other lens systems have similar links between flux-ratio anomalies and disk components. 
}

>>>>

\title[Beware the Effect of Edge-on Disks]{
%Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375
SHARP II: Dark Matter Substructure, Gravitational Lens Flux Ratio
Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
Disks
}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
jwhsueh@ucdavis.edu (JWH); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\\
$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

Gravitational lens flux-ratio anomalies provide a powerful technique
for detecting the presence of dark matter substructure in distant
galaxies.  However, before using the statistics of systems with these
anomalies, it is imperative to ascertain that a given system does not
have properties that could plausibly cause the observed anomaly
without the need for substructure.  In this letter, we present the
case of the B1555+375 lens system, which has a strong radio-wavelength
flux-ratio anomaly but where the lensing galaxy is also revealed in
high-resolution infrared imaging to have a clear edge-on disk component.  The
disk crosses directly over the pair of images that exhibit the
anomaly, and we show that simple models that include the disk can
reproduce the anomaly without requiring substructure.  
Other lens systems that we have observed with adaptive optics imaging
as part of the Strong lensing at High Angular Resolution Programme (SHARP)
show a similar behaviour and will be the subject of a future paper.  
These results suggest that the assumption that
all flux-ratio anomalies are due to substructure will likely overestimate
the substructure fraction in massive galaxies.

@@

It was first suggested by \citet{Mao1998} that flux ratio anomalies
observed in radio loud multiple images of lensed quasar could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are not sensitive to micro lensing from
stars nor dust extinction. This makes flux ratio anomalies a promising
tool to detect dark matter substructures \citep{Dalal2002, N13}.  At
present, the amount of substructure derived from flux ratio anomalies
is in disagreement with predictions from numerical simulations, with
the former requiring a larger fraction of mass in substructure than
expected \citep{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure.
%
An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

While future large-scale surveys, such as the LSST, are expected to
deliver new large samples of gravitationally lensed quasars, in the
near future the discovery of new systems using narrow-line quasar
emission \citep{N14} will provide new invaluable statistical
perspective on current constraints based on flux ratio anomalies.  In
this letter, we explore the idea that not all flux ratio anomalies are
related to the presence of substructure, but that some originate in a
more complex lens galaxy mass distribution than initially
considered. To this end we use new infra-red data from the Strong
lensing at High Angular Resolution Program 
\citep[SHARP;][Fassnacht et al., in prep]{CLASS1}.
The main goal of the SHARP project is to re-observe known
quadruple and Einstein ring lens systems at high angular
resolution by making use of observations with (1) adaptive optics (AO)
on the Keck telescopes, (2) the Hubble Space Telescope, and (3) large
interferometric arrays \citep{SHARP12,V12}. In particular, to better
understand the causes of flux ratio anomalies in gravitational lenses
we focus on the B1555+375 lens system\citep{Marlow99}.  This system was
discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
has a pair of merging images that show a strong flux ratio anomaly at
radio wavelengths.  Follow-up observations ruled out radio propagation
effects as the cause of the anomaly \citep{K03,KD04}.  The B1555+375
system was included in both the observational and theoretical analysis
of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
mass distribution is of key importance.  Our analysis makes use of
the new information obtained from the latest SHARP infrared imaging.
The paper is organized as follows: the  SHARP data are
introduced in section 2; in section 3 we present the lens model while
the results of this analysis and their implications are discussed in
section 4.

@@

To model B1555+375, we use the lens modeling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image
positions and flux densities measured by the radio observations of
\citet{Marlow99}.  These authors present a singular isothermal ellipsoid
(SIE) model that provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A
and B.  \citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  Although
the flux ratio anomaly that is observed in the radio data may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the HST infrared imaging (two rightmost panels in
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux ratio anomaly without the need for substructure.  The edge-on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the lack of detection of these
images.

As a first trial of modelling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, our single elliptical
potential model cannot predict the flux anomaly in B1555+375.  We then
create two separate models of the lensing potential that both
incorporate the disk.  In the first we treat the lens as a SIE bulge
and an exponential edge-on disk (SIE+expdisk).  In the second model
the disk is represented as a very elongated SIE component (2-SIE).
The lens system is red, with a strong jump in flux between the F814W
(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so
we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
$z_s =1.5$. Our steps to explore the parameter space are: (1) Apply
strong priors from SHARP AO image to the edge-on disk position angle
and ellipticity, and use the best-fit model of \citet{Marlow99} as the
starting point for the bulge component and the source position. (2)
Let all parameters without priors vary to reach a temporary best
fit. (3) Start with the best fit in step 2 and let all parameters with
priors vary to reach another best fit (also ensure this best fit is
not far from the priors). (4) Let all parameters vary to reach the
final optimal model.  The full best-fit parameters are shown in Table
2. Both of these models produce lensed images with positions and
fluxes that are good matches to the radio observations.  While both of
the two component models produce significantly improved matches to the
fluxes than the single SIE model, the 2-SIE version has a somewhat
better performance than the SIE+expdisk model in reproducing flux
ratios. The comparison of the observations and our lens modelling is
given in Figure 3 and Tables 3 \& 4.  We have not included an external
shear component into our model because the constraints provided by the
image positions and fluxes would not be sufficient to constrain such a
model. However, we note that the image not affected by dust (image C)
in the Keck AO data is consistent with negligible shear (i.e. shear
strength $\Gamma_s=0.002$), when modelled with the pixelized technique
of \citet{V09}.

@@

Gravitational lensing is, at present, the most powerful tool for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes, such as
propagation effects and assumptions about the mass distribution of the
lens galaxy.  It is for this reason that much of the effort in the
flux-ratio technique has been focused on radio-loud lens systems.  At
these wavelengths, dust extinction and microlensing effects should be
minimal \citep[although see][for a rare example of radio
  microlensing]{K2000}.  Radio propagation effects can affect radio
fluxes, as is clearly shown in the B0128+437 system \citep{B04}.
However, these propagation effects can be disentangled from
substructure lensing because they have well known dependencies on
wavelength. \citet{KD04} examine all eight radio loud flux anomalous
lenses besides B0128+437, namely: MG 0414+0534, B0712+472, B1359+154,
B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265.  They found
no strong wavelength dependence in the flux ratios of all these
systems and therefore rule out radio propagation effects as
significant contributors to the observed anomalies.

In this letter, we focus on the effect of more complicated mass
distributions for the lens galaxy on flux ratio anomalies.
Traditionally, flux anomalous lensed quasars are radio loud systems
that are firstly discovered in radio observations. While radio data
provide reliable information on the positions and the fluxes of the
lensed images, they are often unable to detect the lens
galaxies. Moreover, lens modelling based only on the positions of the
four images can be highly degenerate and prior assumptions play a key
role in the interpretation of the observed flux ratio anomaly.  Since
lens galaxies are typically at redshifts of $z \leq 1$, optical and
near-infrared observations are ideal for measuring the light distribution
of lens galaxies and obtaining useful prior information on the underlying
mass distributions. Indeed \citet{SHARP12} showned that high
resolution IR imaging can help to significantly improve the precision
of the lens modelling. This improvement is even more dramatic in the
case of B1555+375, where HST and SHARP AO high resolution imaging has
allowed us to detect, for the fist time, the presence of an edge-on
disk. This new discovered edge-on disk provides a strong prior for our
lens modelling.  With a bulge plus an edge-on disk, our models produce
matches to both the radio image positions and their flux ratio, while
models with only one SIE component \citep{Marlow99,Xu14} fail to
reproduce the fluxes correctly. Our successful modelling indicates
that the kiloparsec-scale structure of the lens galaxy itself is
sufficient to explain the flux ratio anomalies in B1555+375, without
any need to invoke the presence of substructure.

From a theoretical perspective, \citet{Xu14} also find that substructures
cannot explain the observed radio flux anomalies in all the lenses
that were considered. After adding subhaloes from numerical simulations
to these systems, only one out of the eight radio loud systems
achieves the level of the flux anomalies seen in the observations.  The rest of
them are unlikely (only $1 \% - 4 \%$ probability) to have flux
anomalies produced only by substructure, including our target B1555+375.
In fact, among those eight radio lenses, B1555+375 is one of the most
anomalous systems, but it is also one of the most challenging systems
to explain by substructures. \citet{Xu14} have concluded that the failure in
predicting flux ratios is most likely due to oversimplified/improper lens
modelling. They also point out that the SIE component and the external
shear in their model are orthogonal, indicating a possible missing
ingredient in the lens model. Their results are consistent with the SHARP
$K^{\prime}$ band observations, in which an edge-on disk crosses the
radio merging double and which fully accounts for the observed flux ratio anomaly.  In general, it is well known 
\citep[e.g,][]{Ka91} that lens models based only on the locations of lensed
quasar/AGN images have large degeneracies. Therefore, before
concluding that the flux ratios in any given lens system are a result
of substructure, it is critical to explore a range of smooth models
that are informed by additional observations or to do a comprehensive
analysis such as that conducted by \citet{Xu14}. Otherwise, derived
substructure fractions should be considered as upper limits.

@@

\section{Conclusions}
In this letter we have taken advantage of the power of
multi-wavelength high resolution data to investigate whether flux
ratio anomalies could be explained by more complex smooth models for
the lens galaxy mass distribution rather than substructure. Thanks to
new imaging from the SHARP $K^{\prime}$ band observations of the
gravitational lens system B1555+375, we have identified the existence
of a previously unknown edge-on disk. By including this disk in the
mass model of the lens galaxy, we find a good fit for both the
positions and flux ratios of the lensed images. Our results clearly
demonstrate that the lack of knowledge on the lens galaxy mass
distribution, combined with the limited information provided by the
position of a few lensed images, can lead to improper lens models and
a misinterpretation of the origin of flux ratio anomalies.  We stress,
therefore, that one should be very careful when interpreting the
nature of flux ratio anomalies, as prior assumptions on the lens mass
distribution are a significant source of bias. Our analysis shows that
in order to derive precise quantification of the substructure
population and any derived properties from strongly lensed flux
anomalous systems, it is crucial to have a careful estimation of
non-substructure effects. In fact, even in the presence of mass
substructures, the observed flux ratio anomalies could be still
dominated by the complex structure of the lens galaxy. Finally,
additional near-infrared AO imaging from SHARP shows that B1555+375 is
not the only system having a significant disk component detection in
the lensing galaxy.  These systems will be investigated in future
work, but the images alone strongly suggest that other lens systems
have similar links between flux-ratio anomalies and disk components.
